Collocated Deduplication with Fault Isolation for Virtual Machine Snapshot Backup

### 2013-05-28 snapshot_system/design1.tex
add architecture
change

\section{Prototype Design}

>>>>

\section{Architecture Design}

%\subsection{ Snapshot management}
The virtual device driver uses a bitmap to track the changes that have been made to virtual disk.
Every bit in the bitmap represents a fix-sized (2MB) region called \textit{segment}, indicates whether the segment
is modified since last backup. Hence we could treat segment as the basic unit in snapshot backup similar to
file in normal backup: a snapshot could share a segment with previous snapshot it is not changed. 
Moreover, we break segments into var-sized chunks (average 4KB) using content-based chunking algorithm,
which brings the opportunity of fine-grained deduplication by
allowing data sharing between segments.
The representation of each snapshot has  a two-level index data structure. 
%in the form of a hierarchical directed acyclic graph as shown in Figure \ref{fig:snapshot}.
The snapshot meta data (called snapshot receipe) contains a list of segments, each of which contains segment 
meatdata of its chunks (called segment receipe).

%\begin{figure}[htbp]
%  \centering
%  \epsfig{file=images/snapshot_representation.eps, width=3.7in}
%  \caption{An example of snapshot representation.}
%  \label{fig:snapshot}
%\end{figure}
%We choose this two-level structure because in practice we
%observe that during each backup period only a small amount of VM data are added or modified. 
%As the result, even the metadata of two snapshots can be highly similar, 
%thus aggregating a large number of chunks as one segment can significantly reduce the space cost of snapshot metadata.
%Furthermore, instead of using variables-sized segments, we use a dirty bit to capture the change status of fix-sized
%segments which greatly ease the segment-level deduplication.

In both two kind of recipes, 
they do not include the actual data but only have
 references pointers to the data which are either stored in backup storage or CDS.
In our implementation the data reference is a 8 bytes field which is either an 
ASID (discuss in \ref{sect:append} or an offset of 
An additional flag indicates

### 2013-05-28 snapshot_system/intro.tex
change

The paper proposes an integrated approach which uses  multiple duplicate detection strategies
integrating  version  detection, small-scope inner VM duplicate comparison
and controlled cross-VM comparison. 
The key idea of this approach is to localize duplicate detection within each virtual machine as much as possible
and minimize memory usage while delivering a decent deduplication efficiency. 
That brings the benefits for parallelism  utilization and fault isolation.
Our deletion strategy uses a double Boomer filer strategy for periodic mark-and-sweeping of expired data blocks.
We have developed a prototype system that runs a cluster of Linux machines running Zen.
The backup storage uses a standard distributed file system  with data replication and
we allocate more  replicas for the commonly-shared  data blocks among VM snapshots to enhance fault tolerance.

>>>>

The paper studies and evaluates  an integrated approach which uses  multiple duplicate detection strategies
based on  version  detection, small-scope inner VM duplicate comparison
and controlled cross-VM comparison. 
This approach is VM centric by localizing duplicate detection within each VM  as much as possible
and minimize memory usage while delivering a decent deduplication efficiency. 
That brings the benefits for parallelism  utilization and fault isolation.
Our deletion strategy uses a double Boomer filer strategy for periodic mark-and-sweeping of expired data blocks.
We have developed a prototype system that runs a cluster of Linux machines with Xen.
The backup storage uses a standard distributed file system  with data replication and block packaging,
and we allocate more  replicas for the commonly-shared  data blocks among VM snapshots to enhance fault tolerance.

### 2013-05-28 snapshot_system/main.tex
Append store chapter
add pdf
paper update
chnge
Add cds analysiswq
some changes
rev
analysis
add architecture
change

\documentclass{acm_proc_article-sp}
\usepackage[colorlinks,linkcolor=red,anchorcolor=blue,citecolor=green,urlcolor=black]{hyperref}
\usepackage{epsfig}

@@

\title{An In-Cloud Backup System With Deduplication for VM Snapshot}

\numberofauthors{7}
\author{
\alignauthor Wei Zhang\\
       \affaddr{CS Dept.}\\
       \affaddr{UC Santa Barbara}\\
       \email{wei@cs.ucsb.edu}
\alignauthor Hong Tang\\
       \affaddr{Aliyun Inc.}\\
       \affaddr{Alibaba Group}\\
       \email{hongtang@alibaba-inc.com}
\alignauthor Tao Yang\\
       \affaddr{CS Dept.}\\
       \affaddr{UC Santa Barbara}\\
       \email{tyang@cs.ucsb.edu}
}

@@

% A category with the (minimum) three required fields
\category{H.4}{Information Systems Applications}{Miscellaneous}
%A category including the fourth, optional field follows...
\category{D.2.8}{Software Engineering}{Metrics}[complexity measures, performance measures]

\terms{Theory}

\keywords{ACM proceedings, \LaTeX, text tagging} % NOT required for Proceedings

\input{intro}
\input{design}
\input{snapshot}
\input{append}
\input{cds}
\input{failover}
\input{result}
\input{con}

>>>>

\documentclass{acm_proc_article-sp}
\usepackage[colorlinks,linkcolor=red,anchorcolor=blue,citecolor=green,urlcolor=black]{hyperref}
\usepackage{epsfig}
\usepackage{breqn}

\newcommand{\comments}[1]{}

@@

%\title{Deduplication Localization for Virtual Machine Snapshot Backup}
\title{Collocated Deduplication with Fault Isolation for Virtual Machine Snapshot Backup}
%\title{BigArchive: Low-cost and Scalable Deduplication Storage for VM Snapshot}

\author{
Wei Zhang, Michael Agun,  Tao Yang \\
%Wei Zhang$^{\star}$, Michael Agun,  Tao Yang$^\star$
%{\normalsize$^\star$  University of California at Santa Barbara}, {\normalsize$^\dagger$Alibaba Inc.}
%Wei Zhang, Tao Yang, Gautham Narayanasamy\\
Department of Computer Science\\
University of California,  Santa Barbara, CA 93106
%\and
%Hong Tang\\
%Alibaba Inc.
}
%, Gautham Narayanasamy$^\star$, and Hong Tang$^\dagger$ \\

@@

% A category with the (minimum) three required fields
%\category{H.4}{Information Systems Applications}{Miscellaneous}
%A category including the fourth, optional field follows...
%\category{D.2.8}{Software Engineering}{Metrics}[complexity measures, performance measures]

%\terms{Theory}

%\keywords{ACM proceedings, \LaTeX, text tagging} % NOT required for Proceedings

\input{intro}
%\input{design}
\input{background}
\input{challenge}
\input{snapshot}
\input{failover}
\input{design1}
%\input{snapshot}
%\input{append}\
\input{cds}
%\input{delete}
%\input{failover}
\input{result}
\input{con}

### 2013-05-28 snapshot_system/snapshot.tex
change

\subsection{Snapshot Deduplication and Fault Isolation}
\label{sect:dedupe}
%snapshot representation

@@

Our  deduplication scheme compares the fingerprints of the current snapshot
with its parent snapshot and also other snapshots in the entire cloud.
This process performs   the duplication in two categories: \textit{Inner-VM} and \textit{Cross-VM}. 
Inner-VM duplication exists between VM's snapshots, because the majority of data are unchanged during each backup period. 
Such localization increases data independency between different VM backups,
simplifies snapshot management and statistics collection,
and facilitates parallel execution of snapshot operations.
On the other hand, Cross-VM duplication is mainly due to widely-used software and libraries. 
As the result, different VMs tend to backup large amount of highly similar data.
Our multi-level pipeline process can minimize 
the cost of deduplication while maximize the its efficiency at each level,
and it is parallel since each segment is processed independently.

\begin{itemize}
\item \textbf{Dirty-based corase-grain inner-VM deduplication.}
The first-level deduplication is to follow the standand dirty bit approach, but is conducted
in the coarse grain segment level.
We use the  Xen virtual device driver which supports dirty bits for thestorage device
and the dirty bit setting is maintained in a corase grain level we call it a segment.
In our implementation, the segment size is 2MB. 
Since every write for a block will touch a dirty bit, the device driver maintains dirtybits in memory
and cannot affort a small segment  size.

@@

\item \textbf{Cross-VM deduplication.}
This step accomplishes the standand global fingerprint  comparison as conducted
in the previous work~\cite{??}.
One key observation is that the inner deduplication has removed many of duplicates.
There are not lot of deduplication opportunities cross VMs while the memory
consumption for global comparison is expensive.
Thus our approximation is that duplicate sharing patterns among  VM follows
a zip-like distribution, and the global fingerprint  comparison  only searches
for the most popular items. 
\end{itemize}

@@

{\bf Impact of CDS deduplication.}
Our empirical study based on VM images from production environment\cite{ieeecloud} showed that the
frequency of data duplication follows Zipf-like distribution\cite{zipf},
with the exponent $\alpha$ between 0.65 ~ 0.70.
As a result, it can be proved that deduplication efficiency of CDS index is scalable:

>>>>

\section{Snapshot Deduplication and Fault Isolation}
\label{sect:dedupe}
%snapshot representation

%We use the The deduplication process is first conducted among snapshots within each VM
%and then is conducted across VMs.
%Given the concern that searching duplicates across VMs is a global feature which can affect parallel performance
%and complicate failure management,
%we only eliminate the duplication of a small but popular data set while still maintaining a cost-effective deduplication ratio.
%For this purpose, we exploit the data characteristics of snapshots and collect most popular data.
%Data sharing across VMs is limited within this small data set such that adding replicas for it could enhance fault tolerance

Our  deduplication scheme compares the fingerprints of the current snapshot
with its parent snapshot and also other snapshots in the entire cloud.
This process performs   the duplication in two categories: \textit{Inner-VM} and \textit{Cross-VM}. 
We discuss the integration of several strategies as follows and analyze its effectiveness.

@@

Inner-VM duplication can be effecive within  VM's snapshots because the majority of data are unchanged during each backup period. 
Localizing the snapshot data deduplication witin  a VM first
increases data independency between different VM backups,
simplifies snapshot management and statistics collection,
and facilitates parallel execution of snapshot operations.
On the other hand, cross-VM duplication can also be desirable mainly due to widely-used software and libraries. 
As the result, different VMs tend to backup large amount of highly similar data.
We integrate those strategies together as follows.
%Our multi-level pipeline process can minimize 
%the cost of deduplication while maximize the its efficiency at each level,
%and it is parallel since each segment is processed independently.

\begin{itemize}
\item \textbf{Dirtybit-based corase-grain inner-VM deduplication.}
The first-level deduplication is to follow the standand dirty bit approach, but is conducted
in the coarse grain segment level.
We use the  Xen virtual device driver which supports dirty bits for thestorage device
and the dirty bit setting is maintained in a corase grain level we call it a segment.
In our implementation, the segment size is 2MB. 
Since every write for a block will touch a dirty bit, the device driver maintains dirtybits in memory
and cannot affort a small segment  size.

@@

\item \textbf{Cross-VM deduplication.}
This step accomplishes the standand global fingerprint  comparison as conducted
in the previous work~\cite{??}.
One key observation is that the inner deduplication has removed many of duplicates.
There are not lot of deduplication opportunities cross VMs while the memory
consumption for global comparison is expensive.
Thus our approximation is that the global fingerprint  comparison  only searches for the most popular items. 
%Since duplicate sharing patterns among  VM follows a zip-like distribution,  
\end{itemize}

@@

\subsubsection{Impact of CDS deduplication}
Our empirical study based on VM images from production environment\cite{ieeecloud} showed that the
frequency of data duplication follows Zipf-like distribution\cite{zipf},
with the exponent $\alpha$ between 0.65 ~ 0.70.
As a result, it can be proved that deduplication efficiency of CDS index is scalable:
